Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-08-01 doc/manuscript/manuscript.Rmd
add discussion on dbRDA

## Phenotypic variable assessment {-}

@@

The dbRDA was performed on clone-corrected isolates (N = 318) after grouping them by location, host, region, and year.
The forward-backward selection process revealed severity, year, region, and host to be the optimal variables for the reduced model, accounting for 17.6% of the total variation.
ANOVA revealed that the reduced model was significant with an adjusted R^2^ of 0.033 (P = 0.001).
Assessment of the marginal effects showed that state, host, and year significantly explained genetic variation (P = 0.001), but aggressiveness was only mildly significant (P = 0.045). 
Much of the variation appears to be driven by isolates from Mexico and 2005 (Fig. \@ref(rda-biplot)); it's worth noting that all Mexican isolates were collected in 2005.
Variance partitioning of the independent variables indicated aggressiveness to be the least influential factor with 0.1% contributing to explaining the variation of molecular data whereas the combination of variables accounted for 3.3%.

@@

Of interest in this study was testing the association between mycelial compatibility groups (MCGs) and multilocus genotypes (MLGs).
In the past MCGs have been used as a proxy for clonal lineages [@leslie1993fungal; @otto-hanson2011variation; @kohn1990mycelial; @schafer2006optimized; @kohn1995clonal; @carbone1999patterns]. 
Our results do not support this hypothesis (Fig. \@ref(biggraph)).
Over the past few years, researchers have noticed inconsistencies among the relationship between MCGs and MLGs [@aldrich-wolfe2015genetic; @carbone1999patterns; @attanayake2012genetic; @lehner2015genetic]. 
Either several MCGs belong to one MLG, which could be explained by insufficient sampling of loci; several MLGs belong to one MCG, which could be explained by clonal expansion; or a mixture of both.
Some studies have shown a correlation between MCG and MLG [@aldrich-wolfe2015genetic; @carbone1999patterns; @lehner2015genetic], whereas other studies have shown no apparent correlation, even on small spatial scales [@attanayake2012genetic; @attanayake2013sclerotinia].

@@

>>>>

## Phenotypic Variable Assessment {-}

@@

The dbRDA was performed on clone-corrected isolates (N = 318) after grouping them by location, host, region, and year.
The forward-backward selection process revealed severity, year, region, and host to be the optimal variables for the reduced model, accounting for 17.6% of the total variation.
ANOVA revealed that the reduced model was significant with an adjusted R^2^ of 0.033 (P = 0.001).
Assessment of the marginal effects showed that state, host, and year significantly explained genetic variation (P = 0.001), but aggressiveness was only mildly significant (P = 0.045). 
Much of the variation appears to be driven by isolates from Mexico and 2005 (Fig. \@ref(rda-biplot)).
Variance partitioning of the independent variables indicated aggressiveness to be the least influential factor with 0.1% contributing to explaining the variation of molecular data whereas the combination of variables accounted for 3.3%.

@@

## Phenotypic Variable Importance

Borrowing a technique often used in the ecological literature, we used dbRDA to elucidate the effect of all variables (Aggressiveness, Region, Source,   Year, and Host) [@legendre1999distance].
From the initial results, it appears that the most important factors for predicting genetic structure are region and year.
While the results indicated that Mexico and the year 2005 were the two most important variables, it's worth noting that all Mexican isolates were collected in 2005.
The results also show that the Vista cultivar explains some of the variance, but this represents six isolates in MI. 
Aggressiveness and specific source field had little to no effect on genetic diversity. 
These results are in agreement with studies that examined differentiation based on host [@aldrich-wolfe2015genetic] and severity [@atallah2004high; @attanayake2012genetic; @attanayake2013sclerotinia] reporting little or no correlation of genetic diversity to these variables. 
This indicates that a) breeders should keep in mind regional differences when assessing resistance and b) it is possible that we have not yet measured biologically relevant variables that can predict genetic differentiation, which could include variables such as soil community composition.

## Mycelial Compatibility Groups and Multillocus Genotypes

Of interest in this study was testing the association between mycelial compatibility groups (MCGs) and multilocus genotypes (MLGs).
In the past MCGs have been used as a proxy for clonal lineages [@leslie1993fungal; @otto-hanson2011variation; @kohn1990mycelial; @schafer2006optimized; @kohn1995clonal; @carbone1999patterns]. 
Our results do not support this hypothesis (Fig. \@ref(biggraph)).
Over the past few years, researchers have noticed inconsistencies among the relationship between MCGs and MLGs [@aldrich-wolfe2015genetic; @carbone1999patterns; @attanayake2012genetic; @lehner2015genetic]. 
Either several MCGs belong to one MLG, which could be explained by insufficient sampling of loci; several MLGs belong to one MCG, which could be explained by clonal expansion; or a mixture of both.
Some studies have shown a correlation between MCG and MLG [@aldrich-wolfe2015genetic; @carbone1999patterns; @lehner2015genetic], whereas other studies have shown no apparent correlation, even on small spatial scales [@atallah2004high; @attanayake2012genetic; @attanayake2013sclerotinia].

@@

## Genotypic Structure

## Population Differentiation
